\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-07-11 fluB.tex
Address #13
Not exactly a fix, but some progress towards it.

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.65\textwidth]	{figures/InfB_LineageRatiosOverTime.png}
	\caption{\textbf{Ratio of lineages in the dataset.}
The ratio of sequences that derive from the original Victoria clade (yellow) to sequences that derive from the Yamagata clade (purple) in each segment from the primary dataset over time.
Black lines indicate where this ratio lies in the larger secondary dataset.
Numbers at the top of the figure show the total number of genomes analyzed within each influenza season in the primary dataset comprised of 452 genomes from which the ratio was calculated, while the numbers in brackets correspond to numbers of sequences in the larger secondary genomes dataset.
Numbers at the bottom are influenza seasons from the 1987/1988 (87/88) season to the 2011/2012 season.
Yamagata lineage PA, NP, NA and MP segments and Victoria lineage NS segment eventually become fixed in the influenza B population.
PB1, PB2 and HA segments maintain separate Victoria and Yamagata lineages.}
	\label{lineageRatiosOverTime}
\end{figure}

>>>>

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.65\textwidth]	{figures/InfB_LineageRatiosOverTime.png}
	\caption{\textbf{Ratio of Vic and Yam sequences in the dataset.}
The ratio of Victoria (yellow) to Yamagata (purple) sequences in each segment from the primary dataset over time.
Black lines indicate where this ratio lies in the larger secondary dataset.
Numbers at the top of the figure show the total number of genomes available for each influenza season in the primary dataset comprised of 452 genomes from which the ratio was calculated, while the numbers in brackets correspond to numbers of sequences in the larger secondary genomes dataset.
Numbers at the bottom are influenza seasons from the 1987/1988 (87/88) season to the 2011/2012 season.
Yamagata lineage of PA, NP, NA and MP segments and Victoria lineage of the NS segment eventually become fixed in the influenza B population.
PB1, PB2 and HA segments maintain separate Victoria and Yamagata lineages.}
	\label{lineageRatiosOverTime}
\end{figure}
